Supplement to: Inferring Graphics Programs from Images

### 2017-05-19 synthesizerOutputs.tex
attention citation; improvements to supplement

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,2,3,2,arrow = True,solid = True);
line(6,2,6,3,arrow = False,solid = True);
rectangle(0,0,8,9);
rectangle(5,3,7,6);
reflect(reflect(y = 9)){
line(3,2,5,4,arrow = True,solid = True);
rectangle(1,6,3,8)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(4,2,6,5);
reflect(reflect(y = 7)){
line(2,6,4,4,arrow = True,solid = True);
rectangle(0,5,2,7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(10,5);
line(7,5,9,5,arrow = True,solid = True);
rectangle(0,0,12,10);
reflect(reflect(y = 10)){
line(3,8,5,6,arrow = True,solid = True);
rectangle(1,1,3,3);
rectangle(5,3,7,7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(10,4);
line(10,1,10,3,arrow = False,solid = False);
line(10,1,2,1,arrow = True,solid = False);
line(7,4,9,4,arrow = True,solid = True);
reflect(reflect(y = 8)){
line(2,1,4,3,arrow = True,solid = True);
rectangle(0,6,2,8);
rectangle(4,2,7,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(2,0,5,3);
for (i < 3){
if (i > 0){
line(0,3*i + -2,3*i + -3,4,arrow = False,solid = True);
line(3*i + -3,4,3*i + -1,3,arrow = False,solid = True)
}line(0,1,2,0,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3*i + 7,6);
circle(-3*i + 7,1);
line(-3*i + 7,-1*i + 4,-3*i + 7,5,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,4,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,0,0,0,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,1,5,1,arrow = False,solid = True);
reflect(reflect(x = 7)){
circle(1,1);
line(2,6,5,6,arrow = False,solid = True);
line(1,2,1,5,arrow = False,solid = True);
rectangle(0,5,2,7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(3,2,1,2,arrow = True,solid = True);
line(5,0,3,0,arrow = True,solid = True);
line(2,1,4,1,arrow = True,solid = True);
line(0,3,2,3,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
rectangle(2*i + -2,-2*i + 6,2*i + -1,-2*i + 7)
}rectangle(2*i,-2*i + 6,2*i + 1,-2*i + 7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,3,2,3,arrow = False,solid = False);
line(2,1,4,1,arrow = False,solid = False);
line(1,2,3,2,arrow = False,solid = True);
line(3,0,5,0,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
line(-2*i + 9,3*i,-2*i + 10,3*i + -2,arrow = True,solid = True);
line(-2*i + 9,3*i,-2*i + 8,3*i + -2,arrow = True,solid = True);
rectangle(-2*i + 6,3*i + -3,-2*i + 8,3*i + -1)
}rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
}
        \end{verbatim}
\end{minipage}

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,4,2,2,arrow = True,solid = True);
rectangle(0,0,2,2);
rectangle(3,4,5,6)
        \end{verbatim}
\end{minipage}

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(1,5);
for (i < 3){
if (i > 0){
line(-4*i + 12,1,-4*i + 10,1,arrow = True,solid = True);
rectangle(-4*i + 12,4,-4*i + 14,6)
}line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True);
rectangle(-4*i + 8,0,-4*i + 10,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(4*i,5,4*i + -2,5,arrow = True,solid = True)
}line(4*i + 1,4,4*i + 1,2,arrow = True,solid = True);
rectangle(4*i,0,4*i + 2,2);
rectangle(4*i,4,4*i + 2,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True);
for (j < 2){
circle(-4*i + 9,4*j + 1);
line(-4*j + 8,1,-4*j + 6,1,arrow = True,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
for (i < 3){
if (i > 0){
line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,arrow = True,solid = True);
rectangle(0,-4*i + 11,6,-3*i + 12)
}rectangle(2,0,4,2)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(-3*i + 9,1,-3*i + 8,1,arrow = True,solid = True)
}rectangle(-3*i + 6,0,-3*i + 8,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,3,1,4,arrow = False,solid = True);
for (i < 3){
if (i > 0){
line(1,-5*i + 13,1,-4*i + 10,arrow = True,solid = True)
}circle(1,-4*i + 9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 2)){
line(0,1,1,2,arrow = False,solid = True);
line(1,0,2,1,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,2,2,2,arrow = False,solid = True);
line(0,0,0,2,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(-1*i + 2,i + 4,-2*i + 6,i + 4,arrow = False,solid = True);
line(-1*i + 2,2*i,-1*i + 2,i + 4,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
circle(5,2*i);
circle(1,-3*i + 7);
rectangle(0,-3*i + 6,2,-3*i + 8)
}rectangle(4,1,6,5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(5,5);
line(2,5,4,5,arrow = False,solid = True);
rectangle(0,0,5,3);
rectangle(0,4,2,6)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,6,0,arrow = False,solid = False);
line(0,3,6,3,arrow = False,solid = False);
line(6,0,6,3,arrow = False,solid = True);
line(0,0,0,3,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
circle(5*i + -4,1);
line(i,i + 4,5*i + -4,2,arrow = True,solid = True)
}circle(1,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(-4*i + 9,5*i + -3,-2*i + 7,5,arrow = False,solid = True);
rectangle(-4*i + 8,5*i + -5,6,7*i + -5)
}circle(1,8)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(3*i + 1,1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(2*i,0,2*i + 1,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,5,arrow = False,solid = False);
line(4,1,4,5,arrow = False,solid = False);
line(4,0,4,1,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,5,arrow = False,solid = True);
line(4,0,4,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 12)){
circle(4,1);
line(9,1,10,1,arrow = False,solid = True);
rectangle(10,0,12,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,6,6,6,arrow = True,solid = True);
rectangle(0,4,4,8);
reflect(reflect(y = 12)){
circle(7,6);
line(2,10,2,8,arrow = True,solid = True);
rectangle(1,0,3,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 9)){
line(1,3,1,6,arrow = False,solid = True);
reflect(reflect(y = 9)){
circle(1,8);
line(3,1,6,1,arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 11)){
rectangle(4,1,7,2);
reflect(reflect(x = 11)){
rectangle(1,4,2,7);
rectangle(0,8,3,11)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(-2*i + 5,2*i,-2*i + 7,2*i,arrow = False,solid = True);
line(-2*i + 4,2*i + 1,-2*i + 6,2*i + 1,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
rectangle(-3*i + 10,i + -1,-3*i + 12,2);
rectangle(0,-7*i + 14,3,-7*i + 17)
}rectangle(1,4,2,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(2*i,2*i,2*i + 3,2*i + 1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(4,10);
for (i < 3){
circle(3*i + 1,5);
circle(3*i + 1,1);
line(4,9,3*i + 1,6,arrow = True,solid = True);
line(3*i + 1,4,3*i + 1,2,arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,8,6,4,arrow = True,solid = True);
line(0,8,8,8,arrow = False,solid = True);
line(4,8,4,0,arrow = True,solid = True);
line(2,8,2,6,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,3,2,5,arrow = False,solid = True);
rectangle(0,0,4,8);
reflect(reflect(y = 8)){
rectangle(1,5,3,7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(1,5);
line(1,4,1,2,arrow = True,solid = True);
rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
circle(-4*i + 9,-3*j + 7)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(8,0,8*i + -8,7*i + -7,arrow = True,solid = True)
}rectangle(-2*i + 6,0,-2*i + 7,-1*i + 5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,0,0,0,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(2,1);
circle(6,1);
line(5,1,3,1,arrow = True,solid = True);
rectangle(0,0,7,2)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(5,0,8,3);
rectangle(0,2,1,3);
rectangle(2,1,4,3)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(i,i,-1*i + 5,-1*i + 5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
line(5,2,5,4,arrow = False,solid = True);
reflect(reflect(y = 6)){
line(2,1,4,1,arrow = False,solid = True);
rectangle(4,4,6,6)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
line(1,2,1,4,arrow = False,solid = True);
reflect(reflect(y = 6)){
circle(5,1);
line(2,1,4,1,arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(i,-1*i + 2,-1*i + 7,-1*i + 2,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,4,5,0,arrow = False,solid = True);
line(1,5,5,1,arrow = False,solid = True);
rectangle(0,4,1,5);
rectangle(5,0,6,1)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,4,5,6);
reflect(reflect(x = 5)){
circle(1,1);
line(1,4,1,2,arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
circle(1,9);
for (i < 3){
if (i > 0){
circle(-2*i + 7,-4*i + 9);
line(5,-4*i + 12,-2*i + 7,-4*i + 10,arrow = True,solid = True)
}line(1,8,4,5,arrow = True,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 8)){
for (i < 3){
if (i > 0){
rectangle(3*i + -1,-3*i + 8,3*i,-3*i + 9)
}circle(3*i + 1,-3*i + 7)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
rectangle(2*i + -2,2*i + -2,-2*i + 8,-2*i + 8)
}for (j < 3){
circle(2*j + 1,2*i + 1)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
line(-4*i + 13,4,-4*i + 13,2,arrow = True,solid = True);
for (j < 3){
if (j > 0){
circle(-4*i + 13,-4*j + 9)
}line(-4*j + 10,5,-4*j + 12,5,arrow = True,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,5,4,10,arrow = False,solid = True);
reflect(reflect(x = 8)){
circle(4,1);
circle(1,8);
line(4,5,8,2,arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

>>>>

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,2,6,3,
arrow = False,solid = True);
line(6,2,3,2,
arrow = True,solid = True);
reflect(reflect(y = 9)){
line(3,2,5,4,
arrow = True,solid = True);
rectangle(0,0,8,9);
rectangle(5,3,7,6);
rectangle(1,1,3,3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(4,2,6,5);
reflect(reflect(y = 7)){
line(2,6,4,4,
arrow = True,solid = True);
rectangle(0,0,2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(10,5);
line(7,5,9,5,
arrow = True,solid = True);
rectangle(5,3,7,7);
rectangle(0,0,12,10);
reflect(reflect(y = 10)){
line(3,8,5,6,
arrow = True,solid = True);
rectangle(1,7,3,9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(10,4);
line(10,1,2,1,
arrow = True,solid = False);
line(10,1,10,3,
arrow = False,solid = False);
line(7,4,9,4,
arrow = True,solid = True);
reflect(reflect(y = 8)){
line(2,7,4,5,
arrow = True,solid = True);
rectangle(4,2,7,6);
rectangle(0,6,2,8)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,1,2,0,
arrow = False,solid = True);
for (i < 3){
if (i > 0){
line(3*i + -3,4,3*i + -1,3,
arrow = False,solid = True);
line(0,3*i + -2,3*i + -3,4,
arrow = False,solid = True)
}
rectangle(2,0,5,3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3*i + 7,1);
circle(-3*i + 7,6);
line(-3*i + 7,-1*i + 4,-3*i + 7,5,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,4,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(6,0,0,0,
arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,6,5,6,
arrow = False,solid = True);
reflect(reflect(x = 7)){
circle(6,1);
line(2,1,5,1,
arrow = False,solid = True);
line(1,2,1,5,
arrow = False,solid = True);
rectangle(5,5,7,7)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,1,4,1,
arrow = True,solid = True);
line(3,2,1,2,
arrow = True,solid = True);
line(5,0,3,0,
arrow = True,solid = True);
line(0,3,2,3,
arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
rectangle(-2*i + 6,2*i + -2,-2*i + 7,2*i + -1)
}
rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,3,2,3,
arrow = False,solid = False);
line(2,1,4,1,
arrow = False,solid = False);
line(1,2,3,2,
arrow = False,solid = True);
line(3,0,5,0,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
circle(-2*i + 7,3*i + -2);
line(-2*i + 9,3*i,-2*i + 10,3*i + -2,
arrow = False,solid = True);
line(-2*i + 8,3*i + -2,-2*i + 9,3*i,
arrow = False,solid = True)
}
circle(-2*i + 9,3*i + 1)
}
        \end{verbatim}
\end{minipage}

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
if (i > 0){
line(2*i + 1,-3*i + 12,2*i,-3*i + 10,
arrow = True,solid = True);
line(2*i + 1,-3*i + 12,2*i + 2,-3*i + 10,
arrow = True,solid = True);
rectangle(2*i + -2,-3*i + 9,2*i,-3*i + 11)
}
rectangle(2*i + 2,-3*i + 9,2*i + 4,-3*i + 11)
}
        \end{verbatim}
\end{minipage}

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(5,1);
for (i < 3){
if (i > 0){
circle(7,2*i + -1);
circle(i + 2,2*i + 1)
}
circle(1,6)
}
        \end{verbatim}
\end{minipage}

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,4,2,2,
arrow = True,solid = True);
rectangle(3,4,5,6);
rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,4,2,6);
for (i < 3){
if (i > 0){
line(-4*i + 12,5,-4*i + 10,5,
arrow = True,solid = True);
for (j < i + 1){
circle(-4*j + 9,-4*i + 9)
}
}
line(-4*i + 9,4,-4*i + 9,2,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(-4*i + 9,4,-4*i + 9,2,
arrow = True,solid = True);
for (j < 2){
line(-4*j + 8,5,-4*j + 6,5,
arrow = True,solid = True);
rectangle(-4*i + 8,4*j,-4*i + 10,4*j + 2)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(-4*i + 12,1,-4*i + 10,1,
arrow = True,solid = True)
}
circle(-4*i + 9,1);
circle(-4*i + 9,5);
line(-4*i + 9,2,-4*i + 9,4,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
for (i < 3){
if (i > 0){
line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,
arrow = True,solid = True);
rectangle(0,-4*i + 11,6,-3*i + 12)
}
rectangle(2,0,4,2)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(3*i,1,3*i + -1,1,
arrow = True,solid = True)
}
rectangle(3*i,0,3*i + 2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,3,1,4,
arrow = False,solid = True);
for (i < 3){
if (i > 0){
line(1,-5*i + 13,1,-4*i + 10,
arrow = True,solid = True)
}
circle(1,-4*i + 9)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 2)){
line(0,1,1,2,
arrow = False,solid = True);
line(1,0,2,1,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,0,2,
arrow = False,solid = True);
line(0,2,2,2,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(i,-1*i + 6,2*i + 2,-1*i + 6,
arrow = False,solid = True);
line(i,-2*i + 4,i,-1*i + 6,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
circle(1,-3*i + 7);
circle(5,-2*i + 6);
rectangle(0,-3*i + 6,2,-3*i + 8)
}
rectangle(4,1,6,5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(5,5);
line(2,5,4,5,
arrow = False,solid = True);
rectangle(0,0,5,3);
rectangle(0,4,2,6)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(0,0,6,0,
arrow = False,solid = False);
reflect(reflect(x = 6)){
line(6,0,6,3,
arrow = False,solid = True);
line(0,3,6,3,
arrow = False,solid = False)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
circle(-5*i + 11,1);
line(-1*i + 3,-1*i + 7,-5*i + 11,2,
arrow = True,solid = True)
}
circle(1,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(4*i + -3,-5*i + 12,2*i + 1,5,
arrow = False,solid = True);
rectangle(4*i + -4,-5*i + 10,6,-7*i + 16)
}
circle(1,8)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
circle(-3*i + 7,1)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-2*i + 4,0,-2*i + 5,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,0,4,1,
arrow = False,solid = False);
line(0,0,0,5,
arrow = False,solid = False);
line(4,1,4,5,
arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,0,4,5,
arrow = False,solid = True);
line(0,0,0,5,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 12)){
circle(4,1);
line(9,1,10,1,
arrow = False,solid = True);
rectangle(0,0,2,2)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(0,4,4,8);
reflect(reflect(y = 12)){
circle(7,6);
line(2,2,2,4,
arrow = True,solid = True);
line(4,6,6,6,
arrow = True,solid = True);
rectangle(1,10,3,12)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 9)){
line(3,8,6,8,
arrow = False,solid = True);
reflect(reflect(x = 9)){
circle(1,8);
line(1,3,1,6,
arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 11)){
rectangle(4,9,7,10);
reflect(reflect(x = 11)){
rectangle(1,4,2,7);
rectangle(8,8,11,11)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
line(i,-1*i + 5,i + 2,-1*i + 5,
arrow = False,solid = True);
line(i + 2,-1*i + 3,i + 4,-1*i + 3,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
rectangle(3*i + 1,-1*i + 2,3*i + 3,2);
rectangle(0,7*i + -7,3,7*i + -4)
}
rectangle(1,4,2,6)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-2*i + 4,-2*i + 4,-2*i + 7,-2*i + 5)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(4,10);
for (i < 3){
circle(-3*i + 7,5);
circle(-3*i + 7,1);
line(-3*i + 7,4,-3*i + 7,2,
arrow = True,solid = True);
line(4,9,-3*i + 7,6,
arrow = True,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,8,2,6,
arrow = True,solid = True);
line(6,8,6,4,
arrow = True,solid = True);
line(4,8,4,0,
arrow = True,solid = True);
line(0,8,8,8,
arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(2,3,2,5,
arrow = False,solid = True);
rectangle(1,1,3,3);
rectangle(1,5,3,7);
rectangle(0,0,4,8)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(1,5);
line(1,4,1,2,
arrow = True,solid = True);
rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
for (j < 3){
circle(-4*j + 9,-3*i + 7)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
line(8,0,8*i + -8,7*i + -7,
arrow = True,solid = True)
}
rectangle(2*i + 2,0,2*i + 3,i + 3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(4,0,0,0,
arrow = False,solid = False)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(2,1);
circle(6,1);
line(5,1,3,1,
arrow = True,solid = True);
rectangle(0,0,7,2)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
rectangle(5,0,8,3);
rectangle(2,1,4,3);
rectangle(0,2,1,3)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
rectangle(-1*i + 2,-1*i + 2,i + 3,i + 3)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 6)){
line(5,2,5,4,
arrow = False,solid = True);
reflect(reflect(y = 6)){
line(2,1,4,1,
arrow = False,solid = True);
rectangle(4,4,6,6)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 6)){
line(2,5,4,5,
arrow = False,solid = True);
reflect(reflect(x = 6)){
circle(5,5);
line(1,2,1,4,
arrow = False,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
line(i,-1*i + 2,-1*i + 7,-1*i + 2,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
line(1,4,5,0,
arrow = False,solid = True);
line(1,5,5,1,
arrow = False,solid = True);
rectangle(5,0,6,1);
rectangle(0,4,1,5)
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(x = 5)){
circle(1,1);
line(4,4,4,2,
arrow = True,solid = True);
rectangle(0,4,5,6)
}
        \end{verbatim}
\end{minipage}

@@

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
reflect(reflect(y = 8)){
for (i < 3){
if (i > 0){
rectangle(3*i + -1,2,3*i,3)
}
circle(3*i + 1,3*i + 1)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 3){
if (i > 0){
rectangle(-2*i + 4,-2*i + 4,2*i + 2,2*i + 2)
}
for (j < 3){
circle(-2*i + 5,2*j + 1)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
for (i < 4){
line(-4*i + 13,4,-4*i + 13,2,
arrow = True,solid = True);
for (j < 3){
if (j > 0){
circle(-4*i + 13,4*j + -3)
}
line(-4*j + 10,5,-4*j + 12,5,
arrow = True,solid = True)
}
}
        \end{verbatim}
\end{minipage}

@@

        \begin{minipage}{10cm}
        \begin{verbatim}
circle(4,1);
reflect(reflect(x = 8)){
circle(1,8);
line(4,5,8,2,
arrow = False,solid = True);
line(4,5,4,10,
arrow = False,solid = True)
}
        \end{verbatim}
\end{minipage}
